Approximation as Differentiation notes

### 2025-02-09 notes.tex
Ignore .pdf.

[$\Fam(-,C)$ is a fibred category over $\Set$?]

@@

For a functor $F: C \to Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, x)$ with $I$ an object of $C$ and $x \in FI$
\item morphisms from $(I, x)$ to $(J, y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(x) = y$
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C
\to \Set$. (Where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories.)

In our code we give a slightly different construction. For a category $C$, define the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

>>>>

@@

For a functor $F: C \to Set$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ with $I$ an object of $C$ and $X \in FI$ an $I$-indexed family;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$, in the special case where $F: C
\to \Set$ (where we read a $\Set$-valued functor as a $\Cat$-valued functor restricted to discrete
categories).

In our code we give a slightly different construction, namely the fibred category $\Fam(C)$ over $\Set$ where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}
